Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-13 journal paper/content/sec-intro.tex
cite furman report instead of ACCC report

\xhdr{Economic interpretation: network effects of data.}
\asedit{Our model speaks to policy discussions on regulating data-intensive digital platforms \citep{competition2019digital, scott2019committee}, and particularly to the ongoing debate on the role of data in the digital economy.} One fundamental question in this debate is whether data can serve a similar role as traditional ``network effects", \asedit{creating scenarios when only one firm can function in the market \citep{Rysman09, jullien2019economics}.}
%whereby, when these effects are present, in many cases only one firm can function in the market, leading to competition \emph{for} the market being more important than competition \emph{in} the market \citep{Rysman09, jullien2019economics}.
\asedit{The death spiral/amplification effects mentioned above have a similar flavor as network effects: a relatively small amount of exploration (resp., data advantage)  gets amplified under competition and causes the firm to be starved out of users (resp., take over most of the market).}
%\gaedit{We further find that a small data advantage for one firm gets amplified under competition and leads to that firm taking the entire market, showing that data can provide a similar incumbency advantage as those provided by traditional network effects and can serve as a barrier to entry in online markets.}
A distinctive feature of our approach is that we explicitly model the learning problem of the firms and consider them deploying algorithms for solving this problem.  Thus, we do not explicitly model the network effects, but they arise endogenously from our setup.

>>>>

\xhdr{Economic interpretation: network effects of data.}
\asedit{Our model speaks to policy discussions on regulating data-intensive digital platforms \citep{furman2019unlocking, scott2019committee}, and particularly to the ongoing debate on the role of data in the digital economy.} One fundamental question in this debate is whether data can serve a similar role as traditional ``network effects", \asedit{creating scenarios when only one firm can function in the market \citep{Rysman09, jullien2019economics}.}
%whereby, when these effects are present, in many cases only one firm can function in the market, leading to competition \emph{for} the market being more important than competition \emph{in} the market \citep{Rysman09, jullien2019economics}.
\asedit{The death spiral/amplification effects mentioned above have a similar flavor as network effects: a relatively small amount of exploration (resp., data advantage)  gets amplified under competition and causes the firm to be starved out of users (resp., take over most of the market).}
%\gaedit{We further find that a small data advantage for one firm gets amplified under competition and leads to that firm taking the entire market, showing that data can provide a similar incumbency advantage as those provided by traditional network effects and can serve as a barrier to entry in online markets.}
A distinctive feature of our approach is that we explicitly model the learning problem of the firms and consider them deploying algorithms for solving this problem.  Thus, we do not explicitly model the network effects, but they arise endogenously from our setup.
